There once was a grid at ol' Carkeek

### 2016-08-13 Manuscript/v0.0/carkeek_grid.tex
add environmental sampling methods

%-------------------------------------------------------------------------------
%-----------------------------------METHODS-------------------------------------
%-------------------------------------------------------------------------------
\section*{Methods}
\subsection*{Environmental Sampling}
Starting from lower-intertidal patches of \textit{Zostera marina}, we collected water samples at 1 meter depth from 8 points (0, 75, 125, 250, 500, 1000, 2000, and 4000 meters) along three parallel transects separated by 1000 meters (Figure \ref{site_map}).

>>>>

%-------------------------------------------------------------------------------
%-----------------------------------METHODS-------------------------------------
%-------------------------------------------------------------------------------
\section*{Methods}
\subsection*{Environmental Sampling}
Starting from lower-intertidal patches of \textit{Zostera marina}, we collected water samples at 1 meter depth from 8 points (0, 75, 125, 250, 500, 1000, 2000, and 4000 meters) along three parallel transects separated by 1000 meters (Figure \ref{site_map}).
To destroy residual DNA on equipment used for field sampling and filtration, we washed with a 1:10 solution of household bleach (8.25\% sodium hypochlorite; 7.25\% available chlorine) and deionized water, followed by thorough rinsing with deionized water.
For each environmental sample, water was collected in a clean 1 liter high-density polyethylene bottle, the opening of which was covered with 500 micrometer nylon mesh to prevent entry of larger particles.
Immediately after collecting the sample, the mesh was replaced with a clean lid and the sample was held on ice until filtering.
1 liter from each water sample was filtered in the lab on a clean polysulfone vacuum filter holder fitted with a 47 millimeter diameter cellulose acetate membrane with 0.45 micrometer pores.
Filter membranes were moved into 0.9 milliliters of Longmire buffer (CITE LONGMIRE) using clean forceps.
To test for the extent of wc?(spurious results | contamination) due to laboratory procedures, we filtered three replicate 1 liter samples of deionized water.
These samples were treated identically to the environmental samples throughout the remaining protocols.
